---
title: "Homework 1"
author: "Emily Ogden"
date: "January 10, 2020"
output:
  html_document: default
---
test2
#Part 1
1.
```{r}
strainA=c(0.17,0.2,0.13,0.2,0.24,0.25,0.15,0.21,0.21)
strainB=c(0.47,0.21,0.34,0.32,0.33,0.29,0.18,0.20,0.25)
strainC=c(0.44,0.33,0.37,0.33,0.31,0.27,0.22,0.3,0.28)

```

2.
```{r}
A=mean(strainA)
B=mean(strainB)
A-B
```
3.
```{r}
C=mean(strainC)
C-A
```
4.
```{r}
hist(strainC,xlab =expression(paste("Hydrogen peroxide concentrations (" ,mu, "mol/g)")) ,main = "Common strain ")
```
  
5.
```{r}
Peroxide=c(0.27,0.21,0.34,0.32,0.24,0.29,0.18,0.20,0.29)
Growth.rate=c(1.79,1.01,1.71,1.89,1.41,1.15,1.13,1.20,1.1)
leaf=data.frame("Peroxide"=Peroxide, "Growth.rate"=Growth.rate)
```
6.
```{r}
plot(leaf$Peroxide,leaf$Growth.rate, xlab =expression(paste("Hydrogen peroxide concentrations (" ,mu, "mol/g)")), ylab="Fungal growth rate (cm/day)")
```
  
7.
The growth rate of the fungus increases with increases in the concentration of hydrogen peroxide. This does not support the hypothesis that hydrogen peroxide helps plants defend against fungus.  

#Part 2
8.
```{r}
turtle=read.csv("turtles.csv")
```
9.
```{r}
x=table(turtle$Nesting_status,turtle$Species)
x
```
10.
```{r}
barplot(x,beside = T,col = c("red","green"),xlab="Species",ylab="Frequency",legend.text = T,args.legend = list(x="topleft",bty="n"))
```
  
11.
```{r}
mean(x[2,])
```
```{r}
sd(x[2,])
```
12.
```{r}
HB=x[1,1]/sum(x[,1])
HB
LB=x[1,2]/sum(x[,2])
LB
OR=x[1,3]/sum(x[,3])
OR
```
Species    |Proportions of failed nesting attempts
-----------|-----------------------------------
Hawksbill  | 0.42
Leatherback| 0.33
Olive Ridley| 0.2

I would choose the Hawksbill species to need the greatest conservation efforts, because they have the greatest proportion of failed nesting attempts at 42%.

13.
```{r}
nest=read.csv("nest.csv")
```
14.
```{r}
boxplot(nest[,c(2,3,4)],xlab="Species",ylab="Mean number of eggs laid per beach section")
```
  
15.
```{r}
plot(nest$Leatherback~nest$Hawksbill,xlab="Mean Hawksbill turtle eggs laid per beach section", ylab="Mean Leatherback turtle eggs laid per beach section")
```

